
The new JLab experiment, E08-014, was carried out in Hall A in 2011~\cite{e08014_pr} and focused on the measurements of inclusive cross sections at large $x$ with more statistics and better precision. An high intensity electron beam with a constant energy of $3.356~\mathrm{GeV}$ was employed to strick on a fixed target, and the scattered electrons were simultaneously detected by two identical High-Resolution Spectrometers (HRSs)~\cite{halla_nim}. Each spectrometer consist of a pair of vertical drift chambers (VDCs) for particle tracking, two scintillator planes for triggering and timing measurements, and a gas \v{C}erenkov counter and two layers of lead-glass calorimeters for particle identification. Three 20~cm long cryogenic targets, the liquid $\mathrm{^{2}D}$ , the $\mathrm{^{3}He}$ gas and the $\mathrm{^{4}He}$ gas, were measured, in addition to $\mathrm{^{12}C}$, $\mathrm{^{40}Ca}$ and $\mathrm{^{48}Ca}$. The spectrometers were positioned at $\theta_{0}=21^\circ$, $23^\circ$, $25^\circ$, and $28^\circ$ with total of 9 different central momentum settings, which includes the $\mathrm{Q^{2}}$ range from 1.1~$\mathrm{(GeV/c)^{2}}$ to 2.5~$\mathrm{(GeV/c)^{2}}$ and covers QE region up to $x_{bj}\sim 3$. The detailed description of the experiment and the data analysis can be found in Ref.~\cite{zye_thesis}.

% PID cuts and efficiencies
The electrons were identified by cutting on the calbirated signals of the \v{C}erenkov detector after the alignment of its ten ADC spectra. Additional cuts were applied on the calorimeters signals, including the energy sum normalized by the particle momentum, as well as a graphic cut on the two-dimensional histogram of the first layer's energy vs. the second layer's energy. The efficiencies of these selections are both above 99\% while the pion to electron ratio was estimated to be better than $\mathrm{10^{-4}}$ level due to the low pion production under our kinematic regions. The trigger efficiencies and the detection efficiencies of the \v{C}erenkov detector and calorimeters were carefully evaluated and the results are very close to 100\%.  We only kept events with one-track during the tracking reconstruction since the zero-track and multi-track events were less than 1\%.. 

% Acceptance
The scattered electron's initial momentum, in-plan and out-of-plan angles and its vertex position on the target can be reconstructed with the optics matrices of the HRSs and the tracking information from the VDCs. The optics matrices have been well extracted by many previous Hall A experiments and it were also optimized using the new calibration data taken during our experiment with a 30~cm long optics target composed of 7 carbon foils. The uncertainty from the optics reconstruction is believed to be better than $99\%$~\cite{halla_nim}. We cut on the central region of these reconstructed quantities to choose the best HRS acceptance and ran a Monte Carlo (MC) simulation of the HRSs~\cite{zye_thesis} to correct for the residual acceptance effect which is learnt to be well controlled. (Note: should we discuss the HRS-R Q3 issue and also its uncertainty of Dp correction?)

%targets
For the cryogenic targets, we removed the contaminated events from electrons scattering off the end-cups of the target cells by applying a cut on the reconstructed vertex position of the scattered electron on the target. A dummy target of two thin aluminum foils with 20~cm apart was used to evaluate the level of residual contamination after the cut. With the precise optics reconstruction, a cut of $\pm 7~cm$ at the center part of the target is able to remove $>99.9\%$ of the events from target end-cups.

One of the largest sources of systematic uncertainty come from the non-uniform target densities of $\mathrm{^{2}D}$, $\mathrm{^{3}He}$ and $\mathrm{^{4}He}$ due to the not well distributed coolant flow and the high beam current from $40~mu\mathrm{A}$ up to $120~mu\mathrm{A}$.  We took the boiling study data on these target with varying beam currents, and extrapolated the density profiles when the beam was off and normalized the distribution to the values obtained during the target installation. For safety, we assigned 5\% uncertainty of the target density for each cryogenic target. 

(FIX-HERE: Discuss more about the systematic uncertainties from different sources and make a table).

The cross sections were extracted by binning the data in $x$. A yield ratio method was developed to apply all necessary corrections only on the MC data until the MC yield converges to the experimental yield in the same x bin. The experimental yield for the $ith$ x bin is defined as:
\begin{equation}
Y^{i}_{EX} = \frac{N^{i}_{EX}}{N_{e}},
	\end{equation}
	where $N^{i}_{EX}$ is the number of scattered electrons within the bin after all event selections and acceptance cuts, and $N_{e}$ is the total number of incoming electrons hit on the target. The MC yield can be written as:
	\begin{equation}
	Y^{i}_{MC} = \epsilon_{eff} \cdot \eta_{tg}\cdot \frac{\Delta E'_{MC}\Delta \Omega_{MC}} {N_{MC}^{gen}}\cdot\sum_{j\in i}\sigma^{rad}_{model}(E_{j},E'_{j},\theta_{j}) .
	\label{eqymc}
	\end{equation}
	where $\epsilon_{eff}$ is the product of efficiencies from varied sources. $\eta_{tg}$ denotes the areal density of the scattering centers calculated from the target thickness, $\eta_{tg}=\rho\cdot l \cdot N_{A}/A$ where $N_{A}$ is the Avogadro's number. The target density has been corrected with the boiling effect. $\Delta E'_{MC}$ and $\Delta\Omega_{MC}$ are the momentum and solid angle overages of the HRS in the simulation which were chose to be slighly larger than the actuall ranges, and $N_{MC}^{gen}$ is the total number of generated MC events within the ranges. The terms in $\sum_{j\in i}$ represent that within the $ith$ x-bin, the $jth$ electron is first weighed by the radiated cross section calculated with the incoming beam energy $E_{j}$, outgoing momentum $E'_{j}$ and angle $\theta_{j}$ and then summurized. A cross section model was developed based on the $F(y)$ scaling and the peaking-approximation method was used to calculate the radiation effect~\cite{zye_thesis}. 

	The experimental cross section for the $ith$ x-bin is then given by:
	\begin{equation}
	\sigma_{EX}(E, E'_{i},\theta_{0}) = \frac{Y^{i}_{EX}}{Y^{i}_{MC}}\cdot\sigma_{model}(E, E'_{i},\theta_{0}),
	\end{equation}
	where $E$ is the beam energy fixed at 3.356 GeV, $\theta_{0}$ is the central scattering angle, $E'_{i}$, the scattered energy, is calculated based on $x_{i}$, and $\sigma_{model}(E, E'_{i},\theta_{0})$ is the cross section of the bin calculated from the model with the radiation effect corrected.  In this method, the bin-centering correction was automatically applied for choosing the center of the x-bin. The cross sections of different targets were extracted with exactly the same bins and the same acceptance cuts. Their statistical and systematic errors were individually calculated before taking the cross section ratio.


